### 2025-04-09 index.qmd
rendered the html versions

We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has beeb preregistered at [https://osf.io/6y3dr/](https://osf.io/6y3dr/).

>>>>

We define the aims and methods in [preregistration plan](preregistration/preregistration.qmd), which has been preregistered at [https://osf.io/6y3dr/](https://osf.io/6y3dr/).
